Regular singular Volterra equations on complex domains

### 2023-08-15 reg-sing-volterra.tex
Strengthen statement of thm:example

\begin{lemma}
 For every root of $P$, let $\hat{P}_{\alpha}$ be the Volterra operator

\begin{equation}\label{P-hat_j}
\hat{P}_\alpha:=P(-\zeta)+\partial_{\zeta,\alpha}^{-1}\circ Q(-\zeta)+\partial_{\zeta,\alpha}^{-2}\circ\sum_{r=0}^{d-1}R_r(\partial_{\zeta,\alpha}^{-1})\circ (-\zeta)^r
\end{equation}

If $\hat{\psi}_\alpha$ is a solution of $\hat{P}_\alpha\hat{\psi}_\alpha=0$ then its Laplace transform $\Psi_\alpha:=\laplace_{\zeta,\alpha}^{\theta}\hat{\psi}_\alpha$, defined for a suitable direction $\theta$, is a solution of $\mathcal{P}\Psi_\alpha=0$. By suitable direction, we mean that the ray $\Gamma_{\alpha}^\theta$ must be contained in the domain $\Omega_{\alpha}$. \footnote{The domain $\Omega_{\alpha}$ does not contain the tubular neighborhood of all the other critical points toward infinity as drawn in Section \ref{setting:domain}}.      
\end{lemma}

@@

    \begin{align*}
        \mathcal{P}\Psi_\alpha&=\mathcal{P}\laplace_{\zeta,\alpha}^{\theta}\hat{\psi}_\alpha\\
        &=\laplace_{\zeta,\alpha}^{\theta}\left[P(-\zeta)+\fracderiv{-1}{\zeta}{\alpha}\circ Q(-\zeta)+\fracderiv{-2}{\zeta}{\alpha}\circ\sum_{r=0}^{d-1}R_r(\fracderiv{-1}{\zeta}{\alpha})(-\zeta)^r\right]\hat{\psi}_j\\
        &=\laplace_{\zeta,\alpha}^{\theta}\hat{P}_\alpha\hat{\psi}_\alpha
    \end{align*}
\end{proof}

We can now state and prove the main result of this section, namely that the Volterra operator $\hat{P}_\alpha$ admits a unique solution $\hat{\psi}_\alpha$. %in the function space $(\zeta-\alpha_j)^{\tau_j}+\singexp{\tau_j}{\lambda}(\Omega_j)$.

\begin{thm}\label{thm:example}
    There exists a unique solution of $\hat{P}_\alpha\hat{\psi}_\alpha=0$ such that 
    \[\hat{\psi}_\alpha = f_{0,\alpha}+ f_{\star,\alpha}\]

    where $f_{0,\alpha}$ scales like $\zeta^{\tau_\alpha-1}$ as $\zeta$ goes to $\alpha$ and $f_{\star,\alpha}\in\singexpalg{\tau_\alpha}(\Omega_\alpha)$. The result holds for every critical point of $P$. 
\end{thm}

 \textcolor{magenta}{[In the old version, we need to show somewhere that $\zeta^{\tau_\alpha - 1}$ differs from a multiple of the prototype solution $f_{0,\alpha}$ by an element of $\singexpalg{\tau_\alpha}(\Omega_\alpha)$]}

@@

First of all, we rewrite $\hat{P}_{\alpha}\varphi=0$ as $\varphi = \volterra_\alpha \varphi $: %we introduce the notation $p(a):=P(-\zeta(a))$ and $q(a)=Q(-\zeta(a))$, then $\hat{P}_j$ is

@@

Combining the arguments above, we see as desired that
\[ f_{0, \alpha} \in M\zeta^{\tau_\alpha - 1} + \singexpalg{\tau_\alpha}(\domain_\alpha), \]
with
\[ M = \frac{p(b)}{(\zeta(b)-\alpha)^{\tau_\alpha}}\,b_1^{-1}\,e^{S(b)}. \]

\color{DarkTurquoise}
From Condition~\eqref{cond:sing}, we have
\[ \left| \frac{q}{p}+\frac{\tau_\alpha}{\zeta-\alpha} \right| < \varepsilon \]
in some neighborhood $\domain_\text{near}$ of $\zeta = \alpha$. It follows that
\[ S(a) = \int_{\zeta = \alpha}^a \left[\frac{q}{p}+\frac{\tau_\alpha}{\zeta-\alpha}\right] d\zeta \]
converges for $a \in \domain_\text{near}$, so we have
\[ \exp\left(-\int_b^a\left[\frac{q}{p}+\frac{\tau_\alpha}{\zeta-\alpha}\right] d\zeta\right) = e^{S(b)} e^{-S(a)} \]
for $a \in \domain_\text{near}$. Observe that $|S| \le \varepsilon |\zeta - \alpha|$ in $\domain_\text{near}$.

Since $p$ has a simple zero at $\zeta=\alpha$ The denominator is bounded in some neighbourhood $\domain_{\text{near}}$ of $\zeta=\alpha$
\begin{verify}
By definition of limit, as $\zeta(a)\to\alpha$ we should get
\[
\left\vert\frac{1}{p'(\alpha)+b_2(\zeta(a)-\alpha)+b_3(\zeta(a)-\alpha)^2+...}-\frac{1}{p'(\alpha)}\right\vert\leq \varepsilon
\]
\end{verify}

\[
\frac{1}{|p'(\alpha)+b_2(\zeta(a)-\alpha)+b_3(\zeta(a)-\alpha)^2+...|}\leq  \text{const.} |\zeta(a)-\alpha| + O(|\zeta(a)-\alpha|^2)
\]

Therefore, we deduce from this that
\begin{align*}
f_{0,\alpha} & \in \text{const.}\,(\zeta-\alpha)^{\tau_\alpha-1} + \text{const.}\,(\zeta-\alpha)^{\tau_\alpha-1} O(|\zeta - \alpha|) \\
& \subset \text{const.}\,(\zeta-\alpha)^{\tau_\alpha-1} + \text{const.}\,O\big(|\zeta-\alpha|^{\tau_\alpha}\big) \\
\end{align*}
when we restrict to $\domain_\text{near}$.
\color{black}
\end{proof}

%\color{ForestGreen}
%\begin{align*}
%f & = \volterra f \\
%f_\text{basic} + f_\text{extra} & = \volterra f_\text{basic} + \volterra f_\text{extra} \\
%f_\text{basic} + f_\text{extra} & = \hardpart\,f_\text{basic} + \softpart \,f_\text{basic} + \volterra f_\text{extra} \\
%f_\text{basic} + f_\text{extra} & = f_\text{basic} + \softpart \,f_\text{basic} + \volterra f_\text{extra} \\
%f_\text{extra} & = \softpart \,f_\text{basic} + \volterra f_\text{extra}
%\end{align*}
%Solving the original equation is equivalent to finding a fixed point $f_\text{extra}$ of the affine-linear map
%\[ \varphi \mapsto \softpart\,f_\text{basic} + \volterra \varphi. \]
\bibliographystyle{plain}
\bibliography{airy-resurgence}

>>>>

\begin{lemma}
 For every root $-\alpha$ of $P$, let $\hat{\mathcal{P}}_{\alpha}$ be the Volterra operator

\begin{equation}\label{P-hat_j}
\hat{\mathcal{P}}_\alpha:=P(-\zeta)+\partial_{\zeta,\alpha}^{-1}\circ Q(-\zeta)+\partial_{\zeta,\alpha}^{-2}\circ\sum_{r=0}^{d-1}R_r(\partial_{\zeta,\alpha}^{-1})\circ (-\zeta)^r
\end{equation}

If $\hat{\psi}_\alpha$ is a solution of $\hat{\mathcal{P}}_\alpha\hat{\psi}_\alpha=0$ then its Laplace transform $\Psi_\alpha:=\laplace_{\zeta,\alpha}^{\theta}\hat{\psi}_\alpha$, defined for a suitable direction $\theta$, is a solution of $\mathcal{P}\Psi_\alpha=0$. By suitable direction, we mean that the ray $\Gamma_{\alpha}^\theta$ must be contained in the domain $\Omega_{\alpha}$. \footnote{The domain $\Omega_{\alpha}$ does not contain the tubular neighborhood of all the other critical points toward infinity as drawn in Section \ref{setting:domain}}.      
\end{lemma}

@@

    \begin{align*}
        \mathcal{P}\Psi_\alpha&=\mathcal{P}\laplace_{\zeta,\alpha}^{\theta}\hat{\psi}_\alpha\\
        &=\laplace_{\zeta,\alpha}^{\theta}\left[P(-\zeta)+\fracderiv{-1}{\zeta}{\alpha}\circ Q(-\zeta)+\fracderiv{-2}{\zeta}{\alpha}\circ\sum_{r=0}^{d-1}R_r(\fracderiv{-1}{\zeta}{\alpha})(-\zeta)^r\right]\hat{\psi}_j\\
        &=\laplace_{\zeta,\alpha}^{\theta}\hat{\mathcal{P}}_\alpha\hat{\psi}_\alpha
    \end{align*}
\end{proof}

We can now state and prove the main result of this section, namely that the Volterra operator $\hat{\mathcal{P}}_\alpha$ admits a unique solution $\hat{\psi}_\alpha$. %in the function space $(\zeta-\alpha_j)^{\tau_j}+\singexp{\tau_j}{\lambda}(\Omega_j)$.

\begin{thm}\label{thm:example}
For each root $-\alpha$ of $P$, the equation
\[ \hat{\mathcal{P}}_\alpha \hat{\psi}_\alpha = 0 \]
has a unique solution $\hat{\psi}_\alpha$ in the affine subspace
\[ \zeta^{\tau_\alpha-1} + \singexpalg{\tau_\alpha}(\domain_\alpha) \]
of the space $\singexpalg{\tau_\alpha-1}(\domain_\alpha)$.
%%The equation $\hat{P}_\alpha\hat{\psi}_\alpha=0$ has a unique solution of the form
%%\[ \hat{\psi}_\alpha = \zeta^{\tau_\alpha-1} + f_{\star,\alpha} \]
%%\[\hat{\psi}_\alpha = f_{0,\alpha}+ f_{\star,\alpha}\]
%%where $f_{0,\alpha}$ scales like $\zeta^{\tau_\alpha-1}$ as $\zeta$ goes to $\alpha$ and $f_{\star,\alpha}\in\singexpalg{\tau_\alpha}(\Omega_\alpha)$. The result holds for every critical point of $P$. 
\end{thm}
%%\textcolor{magenta}{[In the old version, we need to show somewhere that $\zeta^{\tau_\alpha - 1}$ differs from a multiple of the prototype solution $f_{0,\alpha}$ by an element of $\singexpalg{\tau_\alpha}(\Omega_\alpha)$]}

@@

First of all, we rewrite $\hat{\mathcal{P}}_{\alpha}\varphi=0$ as $\varphi = \volterra_\alpha \varphi $: %we introduce the notation $p(a):=P(-\zeta(a))$ and $q(a)=Q(-\zeta(a))$, then $\hat{P}_j$ is

@@

Combining the arguments above, we see as desired that
\[ f_{0, \alpha} \in M\zeta^{\tau_\alpha - 1} + \singexpalg{\tau_\alpha}(\domain_\alpha), \]
with
\[ M = \frac{p(b)}{(\zeta(b)-\alpha)^{\tau_\alpha}}\,b_1^{-1}\,e^{S(b)}. \]
\end{proof}

\bibliographystyle{plain}
\bibliography{airy-resurgence}
